### 2020-02-28 CalNotes.tex
CLT - Update

@@

>>>>

Central limit theorem text.
\begin{theorem}\label{thm:CLT} Central limit theorem statement:
	\begin{equation}
		\lim_{\epl \to 0}\lim_{T \to \infty} \sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \Lambda, \quad \text{in law,}
	\end{equation}
	where $\Lambda \sim \mathcal N(0, \Gamma)$ and 
	\begin{equation}
		\Gamma = 2\sigma \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1}\E^{\rho^0}[V'(Z) \otimes V'(Z)]\E^{\rho^0}[V'(X) \otimes V'(Z)]^{-1}.
	\end{equation}
\end{theorem}

\begin{proof} Let us consider the decomposition \eqref{eq:alphaDecomposition}, which yields
	\begin{equation}
		\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) - \sqrt{T} I_2^\epl(T).
	\end{equation}
	\corr{Second term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
	\begin{equation}
	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl_T,
	\end{equation}
	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
	\begin{equation}
	Q^\epl_T \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
	\end{equation}
	is a martingale whose quadratic variation is given by
	\begin{equation}
	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
	\end{equation}
	Since the ergodic theorem guarantees that 
	\begin{equation}
	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
	\end{equation}
	the martingale central limit theorem gives 
	\begin{equation}
	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl_T = \Xi^\epl, \quad \text{in law},
	\end{equation}
	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
	Now, by the ergodic theorem 
	\begin{equation}
	\lim_{T \to \infty} \widetilde M^{-1} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}, \quad \text{a.s.}
	\end{equation}
	Therefore, we have by Slutsky's theorem that
	\begin{equation}
	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
	\end{equation}
	where the covariance matrix $\Gamma^\epl$ is given by
	\begin{equation}
		\Gamma^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
	\end{equation}
	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.

	\corr{Idea for the first term:} Let $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
	\begin{equation}
		\mathcal L^\epl = \begin{pmatrix} -V'(x) - \frac1\epl p'\left(\frac{x}{\epl}\right) \\ \frac1\delta (x - z)	\end{pmatrix} \cdot \nabla_{x, z} + \sigma \partial^2_{xx}.
	\end{equation}
	Then, let $\Phi^\epl$ the solution of the Poisson equation
	\begin{equation}
		\mathcal L^\epl \Phi^\epl(x, z) = V'(z)\frac1\epl p'\left(\frac{x}{\epl}\right) - \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right].
	\end{equation}	
	An application of Itô formula \cite[Remark 6.17]{PaS08} yields
	\begin{equation}
		\frac{1}{T} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t = \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
	\end{equation}
	where the remainder $R_T^\epl$ is given by
	\begin{equation}
		R_T^\epl \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0),
	\end{equation}
	and $S^\epl_T$ is the martingale defined as
	\begin{equation}
		S^\epl_T \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd t.
	\end{equation}
	Therefore, we have
	\begin{equation}
	\begin{aligned}
		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
	\end{aligned}
	\end{equation}
	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get by the ergodic theorem that
	\begin{equation}
		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
	\end{equation}
	Repeating the same reasoning as for $Q_T^\epl$, we get 
	\begin{equation}
		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	\end{equation}
	where the covariance is given by
	\begin{equation}
		\Gamma_1^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
	\end{equation}

@@

\subsection{Central limit theorem}
\begin{figure}[t]
	\centering
	\includegraphics[]{Figures/CLT}
	\caption{Central limit theorem result. The histogram represents numerical results, the solid curve a Gaussian fit to the latter and the dashed curve $\rho_a$ represents the theoretical estimate given in Theorem \ref{thm:CLT}.}
	\label{fig:CLT}
\end{figure}
